---
title: "Exploring the relationship between socioeconomic inequality and urban bird biodiversity across seven global cities using citizen science data"
output:
  pdf_document:
    dev: pdf
    keep_tex: yes
    toc: no
    latex_engine: xelatex
  rtf_document:
    toc: no
  word_document:
csl: /Users/juanrocha/Documents/styles/ecology.csl
bibliography: refs.bib
citecolor: blue
documentclass: article
font: Arial
fontsize: 10pt
linkcolor: blue
urlcolor: blue
header-includes:
- \usepackage{dcolumn, rotating, longtable, lineno, float, array, tabularx, inputenc}
- \setmainfont{Arial}
- \renewcommand{\abstractname}{}
- \graphicspath{{figures/}}
- \usepackage[margin=2.5cm]{geometry}
- \linenumbers
- \usepackage{setspace}
---

```{r warning= FALSE, message = FALSE, include = FALSE}
library(tidyverse)
library(stargazer)
load("results_regressions.Rda")
```

## Introduction

Urban biodiversity provides essential ecosystem services, enhances human well-being, and strengthens the resilience of cities in the face of environmental change [@mcphearson2015; @zari2018importance] (McPhearson et al., 2014; Zari, 2018; Methorst, 2024).
Nevertheless, biodiversity in urban landscapes is increasingly threatened by anthropogenic pressures such as habitat loss, pollution, and climate change (McDonald et al., 2009; Aronson et al., 2014; Keck et al., 2025).
Among the socio-environmental drivers of this decline, socioeconomic inequality has been proposed as a key factor shaping the spatial distribution of biodiversity, contributing to broader patterns of biodiversity loss (Mikkelson et al., 2007; Holland et al., 2009; Hamann et al., 2018).
As global urbanization accelerates, understanding what drives biodiversity patterns in cities becomes critical—not only for ecological sustainability but also for social equity.
Urbanization's effects are not solely physical.
Research has emphasized that a complete understanding of urban ecosystems requires engaging with their socioeconomic dimensions, including city design, demographic concentration, community identity, and inequality (Alberti et al., 2003).
These factors influence biodiversity patterns, which reflect underlying socioeconomic and institutional structures such as income inequality, land-use planning, and urban segregation (Wolch et al., 2014; Aronson et al., 2017).

```{r results='asis', warning=FALSE, message = FALSE, include = FALSE}
stargazer(transpose(sar_fits)$result[[7]], header = FALSE)
```
